---
title       : 7 Number Multiplication Calculator
subtitle    : Coursera Project
author      : James Shepherd
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Purpose of Calculator

The calculator takes 7 numbers and multiplies them together.

Numbers can be entered by using the arrows to increment up or down by 1. 

Alternatively, free text of any value can be input into the boxes.

--- .class #id

## View Results

To view the results, please press the submit button.

The results will be displayed in the right-hand panel.

--- .class #id

## Example Calculation

Example calculation using the 7 default values of 42, 69, 5, 2, 7, 3, 9:

```{r}
42 * 69 * 5 * 2 * 7 * 3 * 9
```

--- .class #id 

## Extensions and Modifications

Modifying the server.R file allows for other mathematical functions to be calculated e.g. addition:

```{r, eval = FALSE}
shinyServer(function(input, output) {
   
  data <- reactive({
    input$numeric + input$numeric2 + input$numeric3 + input$numeric4 + input$numeric5 
    + input$numeric6 + input$numeric7
  })
  
  output$out <- data
  })  
```

Future release will include radio buttons to allow calculations to be changed dynamically by the end user.
